---
title: "Untitled"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(report))
```


I've conducted a study with a mixed design investigating the influence of emotional intelligence (between-subjects factor) on valence and arousal ratings (dependent variables) of positive, negative and neutral images (within-subjects factor).  Since I have two dependent variables that may interrelated, I thought that a MANOVA would be the appropriate test. However, I'm struggling to find online resources on how to run a two-way MANOVA when you have a mixed design (between and within-subjects factors). Could you provide any support on how to conduct this on JASP or SPSS? Alternatively, if you think I should run separate ANOVAs instead, please let me know. 

DVs valence_ratings; arousal_ratings
IVs valence_type ( 3 within); emotional_intelligence (2 between)

valence_ratings + arousal_ratings ~ valence_type + emotional_intelligence


2 between
3 within

```{r}
n_participants=6
n_between_levels = 2
n_within_levels = 3
n_dv = 2

participant_vector <- 
  rep(
    x     = 1:(n_participants * n_between_levels), 
    each  = n_within_levels, 
    times = 1)

set.seed(1234)

data_long <- tibble(
  participant           = participant_vector,
  emote       = rep(c("low", "high"), each=(n_participants*n_within_levels)),
  image       = rep(c("neg", "neutral", "pos"), each=1, times=n_participants*n_between_levels),
  rateVALENCE = rnorm(n=seq_along(participant)),
  rateAROUSAL = rnorm(seq_along(participant)),
)
write_csv(x=data_long, file="data_long.csv")

data_very_wide=data_long %>% 
  pivot_wider(id_cols=c(participant, emote), names_from=image, values_from=c(rateVALENCE, rateAROUSAL))
write_csv(x=data_very_wide, file="data_very_wide.csv")
```

```{r}
data_long
```

```{r}
mod1 <-
  with(data_long, 
       manova(
         cbind(rateVALENCE, rateAROUSAL) ~ emote * image
         )
       )
```

```{r}
anova(mod1)
```

```{r}
report(mod1)
```


